XXX

### 2012-03-25 paper/engNERwiki.tex
abstract

Supervised Named Entity Recogizers require

>>>>

Supervised Named Entity Recogizers require large amount of annotated texts. However, manual annotation is a highly costly procedure, thus reducing the annotation cost is essential. We present a fully automatic method to build NE-annotated corpora from Wikipedia. In contrast to recent work, we apply a new method, which maps the DBpedia classes into CoNLL NE types. Since our method is mainly language-independent, we used it for generating corpora for English and Hungarian, as well. The corpora are freely available.
